\hspace*{-.7em} Analysis of JavaScript Web Applications\\ Using \safe

### 2016-11-12 doc/icse-demo/main.tex
Revised the demo paper.

\begin{abstract}
JavaScript has been the language for web applications, and
the growing prevalence of web environments in various devices
makes JavaScript web applications even more ubiquitous.
However, because JavaScript and web environments are
extremely dynamic, JavaScript web applications are often
vulnerable to type-related errors and security attacks.
To lessen the problem, researchers have developed various analysis
techniques in different analyzers, but such analyzers are not especially
aimed for ease of use by analysis developers.  In this paper, we present \safe, a scalable
analysis framework for ECMAScript especially designed as a playground
for advanced research in JavaScript web applications.  \safe is
light-weight, which supports configurability, extensibility, and
debuggability.
\end{abstract}

@@

To help JavaScript developers build correct programs, researchers
have developed analyzers that support various analysis techniques,
but they are not especially designed for usability.
SAFE\footnote{\url{http://plrg.kaist.ac.kr/redmine/projects/jsf/repository}}~\cite{Lee12}
is a scalable analysis framework for ECMAScript, and it has adopted recent research results incrementally.
While more analysis techniques make SAFE more featureful,
they make the code base of SAFE large and complex, which makes it
difficult for new users to understand the code base.
TAJS\footnote{\url{https://github.com/cs-au-dk/TAJS}}~\cite{TAJSDETER}
is a dataflow analysis for JavaScript that infers type information and call graphs.
It provides an analysis technique as a whole with an option instead of as
configurable components;
for example, the \mtt{-determinacy} option enables the techniques described in~\cite{TAJSDETER}.
WALA\footnote{\url{http://wala.sourceforge.net/wiki/index.php}}~\cite{Schafer13}
was originally developed for pointer analysis of Java programs, and it
also supports flow-insensitive pointer analysis of JavaScript programs.
Because WALA aims to support analysis of multiple programming languages,
the source code repository is huge with many packages.
While SAFE, TAJS, and WALA are mainly static analyzers possibly using dynamic information,
Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
is a dynamic analysis framework for JavaScript, which may miss many execution flows.
It provides simple dynamic analyzers like a taint analyzer as example uses of the framework.

Let us consider SAFE more closely.  It was first designed to analyze pure
JavaScript benchmarks~\cite{Lee12}.  It provides a default static analyzer
based on the abstract interpretation framework, and it supports
flow-sensitive and context-sensitive analyses of stand-alone JavaScript
programs.  It performs several preprocessing steps on JavaScript code to
address some quirky semantics of JavaScript such as the \mtt{with}
statement~\cite{dls13}.
%, and that part has been used by other researchers~\cite{jsai,kjs}.
It was then extended to model web application execution environments
of various browsers~\cite{safewapp} with HTML/DOM tree abstraction,
and it supports analysis of interactions between JavaScript applications
and native functions in platform-specific libraries by using automatic
modeling of library functions from API specifications~\cite{SAFEWAPI}.
Recent extensions of SAFE include aggressive integration of
soundy~\cite{soundy} analysis.  Instead of analyzing the entire concrete
behaviors of programs, it supports an analysis of partial
programs by using approximate call graphs from WALA~\cite{asewala}.
It also utilizes dynamic information statically to focus on specific
environments like specific browser versions~\cite{safehybrid}.
The more advanced analysis techniques SAFE integrates,
the more difficult it is for SAFE users to understand the SAFE code base.

\setcounter{figure}{1}
\begin{figure*}[t]
\centering
\begin{tabular}{c}
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
val commands: List[Command] = List(CmdParse, CmdASTRewrite, CmdCompile, CmdCFGBuild, CmdAnalyze,
                                   CmdBugDetect, CmdHelp)
var phases: List[Phase] = List(Parse, ASTRewrite, Compile, CFGBuild, Analyze, BugDetect, Help)
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (a) Add a new command and a new phase to the lists of available
commands and phases, respectively, in \mtt{Safe.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect) {
  override def display(cfg: CFG): Unit = println(cfg.toString(0))
}
\end{verbatim}
\end{minipage}
\\[1em]
{\small (b) Add the new command by specifying its name and phases in \mtt{Command.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object BugDetect extends PhaseObj[(CFG, Int, CallContext), BugDetectConfig, CFG] {
  val name: String = "bugDetector"
  val help: String = "Detect possible bugs in JavaScript source files."
  def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
    val (cfg, _, _) = in
    // Bug detector implementation here.
    Success(cfg)
  }
  def defaultConfig: BugDetectConfig = BugDetectConfig()
  val options: List[PhaseOption[BugDetectConfig]] = List(
    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
  )
}

@@

\end{verbatim}
\end{minipage}
\\
{\small (c) Implement the new phase in \mtt{phase/BugDetect.scala}}
\end{tabular}
\caption{\small Extension of \safe with a bug detector~\cite{safewapp}}
\label{fig:extensibility}
\end{figure*}

\setcounter{figure}{0}
\begin{figure}[t]
\centering
\begin{tabular}{|c|}\hline
\begin{minipage}{.3\textwidth}
\footnotesize
\begin{verbatim}
Some JSON code
that specifies
the configuration
(phases/options)
of selecting
analysis sensitivity
\end{verbatim}
\end{minipage}
\\\hline
\multicolumn{1}{c}{~}\\[-.7em]
\multicolumn{1}{c}{\small (a) Specifies selected analysis sensitivity}\\
\multicolumn{1}{c}{~}\\[-.7em]
\hline
\begin{minipage}{.3\textwidth}
\footnotesize
\begin{verbatim}
Some JSON code
that specifies
the configuration
(phases/options)
of selecting
abstract domains
\end{verbatim}
\end{minipage}\\\hline
\multicolumn{1}{c}{~}\\[-.7em]
\multicolumn{1}{c}{\small (b) Specifies selected abstract domains}\\
\multicolumn{1}{c}{~}\\[-.7em]
\end{tabular}
\caption{\small \safe analysis configuration files in JSON format}
\label{fig:configurability}
\end{figure}

In this paper, we present \safe, which is aimed to be a playground
for advanced research in JavaScript web applications.  Thus, we
intentionally designed it to be light-weight, highly parametric,
and modular.  The main features of \safe are as follows:
\begin{itemize}
\item Configurability: Because \safe supports various phases
like parsing, compilation, and analysis with many options like
verbosity, pretty printing, and analysis sensitivity, it provides
a declarative way to describe them concisely.

\item Extensibility: In order for researchers to experiment with their
new ideas easily or to reproduce research achievements from the
literature quickly, \safe supports well-designed APIs for adding new
phases or options.

\item Debuggability: To aid \safe users to understand and reason about
analysis results easily, it now supports \htmldebug, which lets users
investigate analysis status from browsers.  \safe has been tested using
Test262, the official ECMAScript conformance suite, and it allows users
to test their experimental analysis techniques with Test262.
\end{itemize}

@@

\subsection{Configurability}
\safe supports various phases, options, and their combinations.
In order to support them, it provides APIs for \safe users to get results
from any phases, and each phase may perform differently depending on
given options.  For example, one may want to compare analysis precision
and scalability with different $n$ for $n$-depth loop unrolling or
different $k$ for $k$-CFA, which distinguishes the same function body
from its different call sites using $k$ call history.  Moreover, \safe even
allows users to experiment with different abstract domains via analysis
options.  For example, while the default abstract domain for strings in
\safe is a string set domain, one may want to try a regular expression
domain~\cite{dls16} or a string automata domain~\cite{aplas14}.

Because specifying various options for different commands as
command-line options multiple times is tedious and error-prone,
we provide an easy way to specify them in a configuration file in
JSON format.  Figure~\ref{fig:configurability}(a) shows an example
configuration file that specifies which analysis sensitivities are to be
used, and the configuration files shown in
Figure~\ref{fig:configurability}(b) specifies which abstract domains
are to be used.  Unlike command-line options,
configuration files enable users to specify the selected options
in a declarative manner.

\subsection{Extensibility}
\setcounter{figure}{2}
\begin{figure*}[t]
\begin{tabular}{c|c|}\cline{2-2}
\begin{minipage}{.52\textwidth}
\includegraphics[width=\textwidth]{seip}
\end{minipage}
&
\begin{minipage}{.44\textwidth}
\small
\begin{verbatim}
sample snapshot
\end{verbatim}
\end{minipage}
\\\cline{2-2}
\end{tabular}
\vspace*{.5em}
\caption{\small Extension of \safe with dynamic heap information~\cite{safehybrid}}
\label{fig:seip}
\end{figure*}

@@

Based on our own painful experiences, we revamped the structures of
the main \safe driver, commands, phases, options, and configurations,
and provide well-designed APIs for adding new commands, phases, and
options.  For example, when we extended \safe with a bug
detector~\cite{safewapp}, all we had to do was to make small
modifications in two files and to implement the bug detector.
Figure~\ref{fig:extensibility}(a) shows how we added a new command
\mtt{CmdBugDetect} and a new phase \mtt{BugDetect} in the main
driver file \mtt{Safe.scala}.  Figure~\ref{fig:extensibility}(b) presents
that we added the new command \mtt{CmdBugDetect} with a name
\mtt{bugDetect} and its phases \mtt{CmdAnalyze >> BugDetect},
which denotes that the new phase \mtt{BugDetect} is added to the end
of the phases of the command \mtt{CmdAnalyze}.  Then,
Figure~\ref{fig:extensibility}(c) shows the implementation of the
bug detector.  While the actual implementation is omitted at line 6,
simply providing its name, help message, configuration, and possible
options all in one single file is enough for \safe to plug the
information into appropriate places.  In this way, users do not
need to understand how \safe handles commands, phases, options, and
help messages, but they can simply specify what they are for the new
command.

Figure~\ref{fig:seip} illustrates another example that we extended \safe
with dynamic heap information as specified in the
literature~\cite{safehybrid}.  The technique is to capture the initial
concrete heap for each browser called \emph{snapshot}, to transform
it to its corresponding abstract heap, to merge the resulting
abstract heap with the default initial heap, and to use the merged heap
for the analysis.  Thus, the implementation of the technique consists
of two parts: a capturing app of concrete heaps, and code that
transforms a concrete heap to an abstract heap and merges it with another
abstract heap.  By using a browser-specific concrete heap
instead of a sound approximation that covers concrete heaps from
all the possible browsers, the technique reduces many false positives
from analysis results.  When applying the technique to \safe, we could
reuse the capturing app in tact, and we had to implement only 
\msf{heap construction} that parses a snapshot and constructs a concrete
heap in \safe, and we could reuse existing APIs for the remaining tasks.
As Figure~\ref{fig:seip} shows, for a given snapshot from the capturing
app, \msf{heap construction} constructs a concrete heap from the
snapshot.  Then, we can use the existing abstraction function for heaps
and the join operation on heaps in \safe.

\subsection{Debuggability}
While many programming language environments provide debugging
facilities, most static analysis frameworks do not provide such utilities
for analysis developers.  Because understanding and reasoning about
analysis status are extremely difficult, tracking the causes of analysis
imprecision is one of the active research topics.  However, existing
JavaScript analyzers are still in pre-mature stages.  \oldsafe provides
a console debugger, which allows users to investigte the analysis status
during analysis with stepwise exeuction of the underlying analyzer.
It indeed helps \oldsafe users debug the analyzer behaviors, but it lacks
documentation and it requires knowledge of the underlying analyzer.

@@

\safe has been tested using Test262, the official ECMAScript
conformance suite:
\begin{center}
\url{https://github.com/tc39/test262}
\end{center}
which helped us find and fix bugs in our modeling of builtin
functions specified in chapter 15 of the ECMAScript
specification~\cite{ECMA}.  Our regression test suite checks
whether the analysis results soundly approximate their corresponding
concrete values.  It also measures how many tests are being analyzed
precisely.  This test infrastructure with Test262 will aid \safe users
who build new analysis techniques to ``test'' the soundness and precision of their
new analysis implementation.

>>>>

\begin{abstract}
JavaScript has been the language for web applications, and
the growing prevalence of web environments in various devices
makes JavaScript web applications even more ubiquitous.
However, because JavaScript and web environments are
extremely dynamic, JavaScript web applications are often
vulnerable to type-related errors and security attacks.
To lessen the problem, researchers have developed various analysis
techniques in different analyzers, but such analyzers are not especially
aimed for ease of use by analysis developers.  In this paper, we present \safe, a scalable
analysis framework for ECMAScript especially designed as a playground
for advanced research in JavaScript web applications.  \safe is
light-weight, which supports pluggability, extensibility, and
debuggability.
\end{abstract}

@@

To help JavaScript developers build correct programs, researchers
have developed analyzers that support various analysis techniques,
but they are not especially designed for usability.
SAFE\footnote{\url{https://github.com/sukyoung/safe/tree/SAFE1.0}}~\cite{Lee12}
is a scalable analysis framework for ECMAScript, and it has adopted recent research results incrementally.
While more analysis techniques make SAFE more featureful,
they make the code base of SAFE large and complex, which makes it
difficult for new users to understand the code base.
TAJS\footnote{\url{https://github.com/cs-au-dk/TAJS}}~\cite{TAJSDETER}
is a dataflow analysis for JavaScript that infers type information and call graphs.
Even though it provides a large collection of analysis techniques like SAFE,
it does not provide a facility to understand the analysis status during analysis.
Similarly for SAFE, it is not easy for a novice user to extend TAJS to
experiment with new analysis techniques.
%{\color{red}{
%It provides an analysis technique as a whole with an option instead of as
%configurable components.  For example, because the \mtt{-determinacy} option
% enables the techniques described in~\cite{TAJSDETER} altogether,
% it does not provide a way to experiment with each technique separately.}}
%
WALA\footnote{\url{http://wala.sourceforge.net/wiki/index.php}}~\cite{Schafer13}
was originally developed for pointer analysis of Java programs, and it
also supports flow-insensitive pointer analysis of JavaScript programs.
Because WALA aims to support analysis of multiple programming languages,
the source code repository is gigantic with many packages,
which incurs a huge learning curve.
% While SAFE, TAJS, and WALA are mainly static analyzers possibly using dynamic information,
% Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
% is a dynamic analysis framework for JavaScript, which may miss many execution flows.
% It provides simple dynamic analyzers like a taint analyzer as example uses of the framework.

The more advanced analysis techniques are integrated,
the more difficult it is for analyzer users to understand the code base.
For example, SAFE was first designed to analyze pure
JavaScript benchmarks~\cite{Lee12}.  It provides a default static analyzer
based on the abstract interpretation framework, and it 
performs several preprocessing steps on JavaScript code to
address quirky semantics of JavaScript such as the \mtt{with}
statement~\cite{dls13}.
%, and that part has been used by other researchers~\cite{jsai,kjs}.
It was then extended to model web application execution environments
of various browsers~\cite{jswapp} with HTML/DOM tree abstraction,
and it supports analysis of interactions between JavaScript code
and native functions in platform-specific libraries by using automatic
modeling of library functions from API specifications~\cite{SAFEWAPI}.
Recent extensions of SAFE include aggressive integration of
soundy~\cite{soundy} analysis.  Instead of analyzing the entire concrete
behaviors of programs, it supports an analysis of partial
programs by using approximate call graphs from WALA~\cite{asewala}.
It also utilizes dynamic information statically to focus on specific
environments like specific browser versions~\cite{safehybrid}.
The more features are integrated, the more complicated the SAFE code base gets.

\setcounter{figure}{1}
\begin{figure*}[t]
\centering
\begin{tabular}{c}
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
val commands: List[Command] = List(CmdParse, CmdASTRewrite, CmdCompile, CmdCFGBuild, CmdAnalyze,
                                   CmdBugDetect, CmdHelp)
var phases: List[Phase] = List(Parse, ASTRewrite, Compile, CFGBuild, Analyze, BugDetect, Help)
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (a) Add a new command and a new phase to the lists of available
commands and phases, respectively, in \mtt{Safe.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect) {
  override def display(cfg: CFG): Unit = println(cfg.toString(0))
}
\end{verbatim}
\end{minipage}
\\[1em]
{\small (b) Add the new command by specifying its name and phases in \mtt{Command.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object BugDetect extends PhaseObj[(CFG, Int, CallContext), BugDetectConfig, CFG] {
  val name: String = "bugDetector"
  val help: String = "Detect possible bugs in JavaScript source files."
  def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
    val (cfg, _, _) = in
\end{verbatim}
\vspace*{-.6em}
\textbf{~~~~~~~// Bug detector implementation here.}
\vspace*{-.8em}
\begin{verbatim}
    Success(cfg)
  }
  def defaultConfig: BugDetectConfig = BugDetectConfig()
  val options: List[PhaseOption[BugDetectConfig]] = List(
    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
  )
}

@@

\end{verbatim}
\end{minipage}
\\
{\small (c) Implement the new phase in \mtt{phase/BugDetect.scala}}
\end{tabular}
\caption{\small Extension of \safe with a bug detector~\cite{jswapp}}
\label{fig:extensibility}
\end{figure*}

\setcounter{figure}{0}
\begin{figure}[t]
\centering
\begin{tabular}{|c|}\hline
\begin{minipage}{.3\textwidth}
\footnotesize
\vspace*{.3em}
\begin{verbatim}
{
  "analyzer": {
    "callsiteSensitivity": 1
  },
  "file": ["wikipedia.org.htm"]
}
\end{verbatim}
\vspace*{.05em}
\end{minipage}
\\\hline
\multicolumn{1}{c}{~}\\[-.7em]
\multicolumn{1}{c}{\small (a) Specifies selected analysis sensitivity}\\
\multicolumn{1}{c}{~}\\[-.7em]
\hline
\begin{minipage}{.3\textwidth}
\footnotesize
\vspace*{.3em}
\begin{verbatim}
{
  "analyzer": {
    "number": "flat",
    "maxStrSetSize": 10
  },
  "file": ["wikipedia.org.htm"]
}
\end{verbatim}
\vspace*{.05em}
\end{minipage}\\\hline
\multicolumn{1}{c}{~}\\[-.7em]
\multicolumn{1}{c}{\small (b) Specifies selected abstract domains}\\
\multicolumn{1}{c}{~}\\[-.7em]
\end{tabular}
\caption{\small \safe analysis configuration files in JSON format}
\label{fig:pluggability}
\end{figure}

In this paper, we present \safe\footnote{
\url{https://github.com/sukyoung/safe}}, a playground
for advanced research in JavaScript web applications\footnote{
We call SAFE ``\oldsafe'' from now on to distinguish it from \safe.
}.  We designed it to be light-weight, highly parametric,
and modular.  \safe has the following main features:
\begin{itemize}
\item Pluggability: To help analysis developers experiment with
various analysis techniques easily, \safe enables analysis sensitivities
and even abstract domains to be selected at run time.

\item Extensibility: In order for researchers to implement their
new ideas easily or to reproduce research achievements from the
literature quickly, \safe supports well-designed APIs for adding new
phases or options.

\item Debuggability: To aid \safe users to understand and reason about
analysis results easily, it supports \htmldebug, which lets users
investigate analysis status from browsers.  Users can also
test their analysis implementation with Test262,
the official ECMAScript conformance suite.
\end{itemize}

@@

\subsection{Pluggability}
\safe is designed to support selection of analysis sensitivities and
abstract domains at run time.  A large body of research on program
analysis has been designing, developing, and evaluating various
analysis techniques like analysis sensitivities and abstract domains.
For example, researchers have evaluated the analysis precision
and scalability with different $n$ for $n$-depth loop unrolling or
different $k$ for $k$-CFA, which distinguishes the same function body
from its different call sites using $k$ call history~\cite{SAFELSA}.
Moreover, various abstract domains for JavaScript string analysis
have been proposed such as a regular expression
domain~\cite{dls16} and a string automata domain~\cite{aplas14}.
However, with existing analyzers, it is not easy to configure analysis
sensitivities and abstract domains without recompilation of the analyzers.

In order to help analysis researchers experiment with different analysis
techniques easily, \safe provides APIs that support pluggable analysis
sensitivities and abstract domains.  The APIs enable \safe users
to select specific analysis techniques.  For example, while the default
abstract domain for strings in \safe is a string set domain, one can use
a regular expression domain or a string automata domain.
Because specifying various selection as command-line options multiple
times is tedious and error-prone, we provide an easy way to specify them
in a configuration file in JSON format.
The configuration file shown in Figure~\ref{fig:pluggability}(a)
specifies that it uses the 1-CFA analysis sensitivity, and the one in
Figure~\ref{fig:pluggability}(b) specifies that it uses a flat number
domain and a string set domain of maximum size 10.

% \safe supports various phases, options, and their combinations.
% In order to support them, it provides APIs for \safe users to get results
% from any phases, and each phase may perform differently depending on
% given options.  For example, one may want to compare analysis precision
% and scalability with different $n$ for $n$-depth loop unrolling or
% different $k$ for $k$-CFA, which distinguishes the same function body
% from its different call sites using $k$ call history.  Moreover, \safe even
% allows users to experiment with different abstract domains via analysis
% options.  For example, while the default abstract domain for strings in
% \safe is a string set domain, one may want to try a regular expression
% domain~\cite{dls16} or a string automata domain~\cite{aplas14}.

% Because specifying various options for different commands as
% command-line options multiple times is tedious and error-prone,
% we provide an easy way to specify them in a configuration file in
% JSON format.  Figure~\ref{fig:pluggability}(a) shows an example
% configuration file that specifies which analysis sensitivities are to be
% used, and the configuration files shown in
% Figure~\ref{fig:pluggability}(b) specifies which abstract domains
% are to be used.  Unlike command-line options,
% configuration files enable users to specify the selected options
% in a declarative manner.

\subsection{Extensibility}
\setcounter{figure}{2}
\begin{figure*}[t]
\hspace*{-1em}
\begin{tabular}{cc}
\begin{tabular}{c}
\begin{minipage}{.5\textwidth}
\includegraphics[width=\textwidth]{seip}
\end{minipage}
\\\\[-.5em]
\multicolumn{1}{c}{\small (a) Use of dynamic heap information to reduce false positives~\cite{safehybrid}}\\
\end{tabular}
&
\begin{tabular}{c}
\begin{minipage}{.45\textwidth}
\footnotesize
\begin{verbatim}
def addSnapshot(st: AbsState,
                snapshot: String): AbsState = {
  val concreteHeap = Heap.parse(snapshot)
  val abstractHeap = AbsHeap.alpha(concreteHeap)
  AbsState(st.heap + abstractHeap, st.context)
}
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (b) Implement the new technique}
\\[1em]
\begin{minipage}{.45\textwidth}
\footnotesize
\begin{verbatim}
("snapshot",
 StrOption((c, s) => c.snapshot = Some(s)),
 "analysis with an initial heap generated \
  from a dynamic snapshot(*.json)."),

config.snapshot.map(str =>
  initSt = Initialize.addSnapshot(initSt, str))
\end{verbatim}
\end{minipage}
\\\\[-.5em]
{\small (c) Add a new option in \mtt{Analyze.scala}}
\\[.5em]
\end{tabular}
%\begin{minipage}{.4\textwidth}
%\footnotesize
%\vspace*{.3em}
% \begin{verbatim}
% {
%   "#Global": {
%     "chrome": {
%       "value": "#Chrome",
%       "writable": true,
%       "enumerable": true,
%       "configurable": false
%     }
%   },
%   "#Chrome": {
%     "[[Extensible]]": true,
%     "[[Prototype]]": "#Object.prototype",
%     "[[Class]]": "Object"
%   }
% }
% \end{verbatim}
%\vspace*{.1em}
%\end{minipage}
\end{tabular}
\caption{\small Extension of \safe with dynamic heap information~\cite{safehybrid}}
\label{fig:seip}
\end{figure*}

@@

Based on our own painful experiences, we revamped the structures of
the main \safe driver, commands, phases, options, and configurations,
and provide well-designed APIs for adding new commands, phases, and
options.  For example, when we extended \safe with a bug
detector~\cite{jswapp}, all we had to do was to make small
modifications in two files and to implement the bug detector.
Figure~\ref{fig:extensibility}(a) shows how we added a new command
\mtt{CmdBugDetect} and a new phase \mtt{BugDetect} in the main
driver file \mtt{Safe.scala}.  Figure~\ref{fig:extensibility}(b) presents
that we added the new command \mtt{CmdBugDetect} with a name
\mtt{bugDetect} and its phases \mtt{CmdAnalyze >> BugDetect},
which denotes that the new phase \mtt{BugDetect} is added to the end
of the phases of the command \mtt{CmdAnalyze}.  Then,
Figure~\ref{fig:extensibility}(c) shows the implementation of the
bug detector.  While the actual implementation is omitted,
simply providing its name, help message, configuration, and possible
options all in one single file is enough for \safe to plug the
information into appropriate places.  In this way, users do not
need to understand how \safe handles commands, phases, options, and
help messages, but they can simply specify what they are for the new
command.

Figure~\ref{fig:seip} illustrates another example extending \safe
with dynamic heap information as specified in the
literature~\cite{safehybrid}.  The technique is to capture the initial
concrete heap for each browser called \emph{snapshot}, to transform
it to its corresponding abstract heap, to merge the resulting
abstract heap with the default initial heap, and to use the merged heap
for the analysis.  Thus, the implementation of the technique consists
of two parts: a capturing app of dynamic heap, and code that
transforms the captured dynamic heap to an abstract heap and merges it
with another abstract heap.  By using a browser-specific information
instead of a sound approximation of all browsers, the technique reduces many false positives
from analysis results.  When applying the technique to \safe,
we had to implement only \mtt{Heap.parse} that parses a snapshot and
constructs a concrete heap in \safe, and we could reuse the capturing app in tact
and existing \safe APIs for the remaining tasks.
As Figure~\ref{fig:seip}(b) shows, for a given snapshot from the capturing
app, \mtt{Heap.parse} constructs a concrete heap from the
snapshot.  Then, we can use the existing abstraction function for heaps
\mtt{AbsHeap.alpha} and the join operation on heaps \mtt{+} in \safe.
As Figure~\ref{fig:seip}(c) shows, one can add a new technique
to the existing analysis by simply adding one option.

\subsection{Debuggability}
While many programming language environments provide debugging
facilities, most static analysis frameworks do not provide such utilities
for analysis developers.  Because understanding and reasoning about
analysis status are extremely difficult, tracking the causes of analysis
imprecision is one of the active research topics.  However, existing
JavaScript analyzers are still in pre-mature stages.  \oldsafe provides
a console debugger, which allows users to investigate the analysis status
during analysis with stepwise execution of the underlying analyzer.
It indeed helps \oldsafe users debug the analyzer behaviors, but it lacks
documentation and it requires knowledge of the underlying analyzer.

@@

\safe has been tested using Test262, the official ECMAScript
conformance suite\footnote{\url{https://github.com/tc39/test262}},
which helped us find and fix bugs in our modeling of builtin
functions specified in chapter 15 of the ECMAScript
specification~\cite{ECMA}.  Our regression test suite checks
whether the analysis results soundly approximate their corresponding
concrete values.  It also measures how many tests are being analyzed
precisely.  This test infrastructure with Test262 will aid \safe users
who build new analysis techniques to ``test'' the soundness and precision of their
new analysis implementation.
